First steps towards a formalization of Forcing

### 2018-06-24 LSFA/names.tex
edicion global
notacion

\section{Names}

The forcing idea consists of finding a model extending $M$ such that
it satisfies $ZFC + \neg CH$. This model is called the $\textit{generic extension}$
$M[G]$, where $G$ is a \emph{$\calD$-generic} filter in $P$.

@@

This definition proceeds by well-founded recursion on relation $edrel(eclose(M))$:

@@

    $\langle \sigma , \tau \rangle \in edrel(Memrel(M)) $ iff $\langle \sigma , p \rangle \in \tau$ with $p \in G$.

>>>>

\section{Names}
\label{sec:names}

The forcing idea consists of finding a model extending $M$ such that
it satisfies $\ZFC + \neg \CH$. This model is called the $\textit{generic extension}$
$M[G]$, where $G$ is a \emph{$\calD$-generic} filter in $P$.

@@

This definition proceeds by well-founded recursion on relation $\edrel(\eclose(M))$:

@@

    $\langle \sigma , \tau \rangle \in \edrel(\Memrel(M)) $ iff $\langle \sigma , p \rangle \in \tau$ with $p \in G$.
